\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-09 paper.tex
Hice los cambios y modificaciones de la celda, los estilo de letra de los pie de imagenas

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory

@@

  \includegraphics[scale=.6]{Images/celd1}
  \caption{\emph{Diagram shows that there is a positive (real) plane $

@@

      with the period $ L_z = 4c $}}

@@

  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for

@@

      different regions as mentioned above. }}

@@

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PS), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

	\includegraphics[scale=.3]{Images/celdan2}
	\caption{\emph{ Mechanical 3D modeling, design of the

@@

            without top cover and c) Top view}}

@@

  \includegraphics[scale=.5]{Images/SPgrin51}
  \caption{\emph{a) Silicon sample attacked with an electrolytic

@@

      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }

@@

  \includegraphics[scale=.5]{Images/semD11}
  \caption{\emph{Characterization of a monolayer of PS GRIN G1

@@

      \ \ nm $ } }

@@

   \includegraphics[scale=.7]{Images/grinJDR}
   \caption{\emph{a) It is the relation of the current density $

@@

       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ } }

@@

  \includegraphics[scale=.6]{Images/grinJD31}
  \caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $

@@

      the manufacture of any GRIN porous silicon structure   } }

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[scale=0.4]{Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{_{Hi}}$ and low (L) refractive index
            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
            is the monolayer thickness of $n_{_{Hi}}$ at that
            measurement point. Therefore,  $d_{_{i}}$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
the monolayer thickness of $n_{_{Hi}}$ at that measurement
point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_{_{i}} =
(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[scale=.5]{Images/MCGRIN2}
  \caption{\emph{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }}
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[scale=.5]{Images/MCGRINSEM}
   \caption{\emph{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_{_{i}} =
       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
	\label{fig:MCGRIN4}
\end{figure}

@@

\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun,
  P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent
    optics derived from porous silicon.}\textquotedblright ACS
  Photonics, 4(4), 909-914.
\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
  \emph{Root Mean Square Roughness of Nano Porous Silicon by
    Scattering Spectra.}\textquotedblright The
  European Physical Journal Plus 129: 129.
\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft
  \emph{Roughness of the Porous Silicon Dissolution
    Interface.}\textquotedblright Journal of Applied Physics 81:
  61716178.
\bibitem{I19} Lérondel G, Romestain R, Barret S
  (1997).\textquotedblleft \emph{Quantitative Analysis of the Light
    Scattering Effect on Porous Silicon
    Optical Measurements.}\textquotedblright Thin Solid Films 297:
  114?117.

\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,
  A. \textquotedblleft  \emph{Direct characterization of states and
    modes in defect grating structures.}\textquotedblright
  J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.

>>>>

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory \cite{T1,T2}

@@

  \includegraphics[width=\textwidth]{Images/celd1}
  \caption{Diagram shows that there is a positive (real) plane $

@@

      with the period $ L_z = 4c $}

@@

  \includegraphics[width=\textwidth]{Images/DE1}
\caption{Schematic of the experimental set-up for

@@

      different regions as mentioned above. }

@@

\section{Discussion and Results}
\subsection{Simulation of  the current density}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/G123}
  \caption{Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PS), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $ Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

	\includegraphics[width=\textwidth]{Images/celdan2}
	\caption{Mechanical 3D modeling, design of the

@@

            without top cover and c) Top view}

@@

  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{a) Silicon sample attacked with an electrolytic

@@

      (P = 0.44), B (P = 0.42) and C (P = 0.40) }

@@

  \includegraphics[width=\textwidth]{Images/semD11}
  \caption{Characterization of a monolayer of PS GRIN G1

@@

      \ \ nm $ }

@@

   \includegraphics[width=\textwidth]{Images/grinJDR}
   \caption{a) It is the relation of the current density $

@@

       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ }

@@

  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{The relationship of samples $ G1 (I = 5 mA) $ and $

@@

      the manufacture of any GRIN porous silicon structure   }

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Images/MicrGrin}
	\caption{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{_{Hi}}$ and low (L) refractive index
            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
            is the monolayer thickness of $n_{_{Hi}}$ at that
            measurement point. Therefore,  $d_{_{i}}$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
the monolayer thickness of $n_{_{Hi}}$ at that measurement
point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_{_{i}} =
(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_{_{i}} =
       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
	\label{fig:MCGRIN4}
\end{figure}

@@

\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun,
  P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent
    optics derived from porous silicon.}\textquotedblright ACS
  Photonics, 4(4), 909-914.

  \bibitem{T1}Jackson, John David. \textquotedblleft 
  \emph{Classical electrodynamics.}\textquotedblright (1999): 841-842.

\bibitem{T2}Griffiths, David J. \textquotedblleft 
\emph{Introduction to electrodynamics.}\textquotedblright 
 New Jersey: Prentice Hall, 1962.

\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
  \emph{Root Mean Square Roughness of Nano Porous Silicon by
    Scattering Spectra.}\textquotedblright The
  European Physical Journal Plus 129: 129.
\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft
  \emph{Roughness of the Porous Silicon Dissolution
    Interface.}\textquotedblright Journal of Applied Physics 81:
  61716178.
\bibitem{I19} Lérondel G, Romestain R, Barret S
  (1997).\textquotedblleft \emph{Quantitative Analysis of the Light
    Scattering Effect on Porous Silicon
    Optical Measurements.}\textquotedblright Thin Solid Films 297:
  114?117.

\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}
\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,
  A. \textquotedblleft  \emph{Direct characterization of states and
    modes in defect grating structures.}\textquotedblright
  J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.
